uncontrolled

### 2022-09-19 inst/examples/author_name.Rmd
Slight changes to scripts for bookdown compatibility

---
title: "author_name"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$author_name)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

---
title: "author_Name"
output: md_document
---

# Author's name

```{r setup-author-name, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-author-name, include=FALSE}
# author_name field
source("author_name.R")
```

@@

```{r summarytitle-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "author_name", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$author_name)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/corporate.Rmd
change
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "corporate", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$corporate)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

# Corporate

```{r setup-corporate, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-corporate, include=FALSE}
# corporate field
source("corporate.R")
```

[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

@@

```{r summarytitle-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "corporate", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$corporate)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/holder.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "holder", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$holder)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

# Holder

```{r setup-holder, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-holder, include=FALSE, eval=knit_bookdown}
# holder field
source("holder.R")
```

@@

```{r summarytitle-holder, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "holder", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-holder, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$holder)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/note_510c.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_510c", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_510c)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-note-510c, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-note-510c, include=FALSE, eval=knit_bookdown}
# note_510c field
source("note_510c.R")
```

# Note 510C

@@

```{r summarytitle-note-510c, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_510c", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-note-510c, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_510c)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/note_dissertation.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_dissertation", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_dissertation)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-note-dissertation, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-note-dissertation, include=FALSE, eval=knit_bookdown}
# note_dissertation field
source("note_dissertation.R")
```

# Note dissertation

@@

```{r summarytitle-note-dissertation, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_dissertation", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-note-dissertation, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_dissertation)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/note_granter.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```
* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_granter", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_granter)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-note-granter, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-note-granter, include=FALSE, eval=knit_bookdown}
# note_granter field
source("note_granter.R")
```

# Note granter

* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)

@@

```{r summarytitle-note-granter, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_granter", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-note-granter, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_granter)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/note_source.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_source", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_source)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-note-source, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-note-source, include=FALSE, eval=knit_bookdown}
# note_source field
source("note_source.R")
```

# Note source

@@

```{r summarytitle-note-source, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_source", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-note-source, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_source)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/publication_interval.Rmd
change
Slight changes to scripts for bookdown compatibility

---
title: "Publication interval summaries"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publication interval

>>>>

---
title: "Publication interval summaries"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: md_document
---

```{r source-publication-interval, include=FALSE, eval=knit_bookdown}
#publication_interval field
source("publication_interval.R")
```

# Publication interval

### 2022-09-19 inst/examples/publication_place.Rmd
Slight changes to scripts for bookdown compatibility

---
title: "Publication place preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publication places

>>>>

---
title: "Publication place preprocessing summary"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r source-publication-place, include=FALSE, eval=knit_bookdown}
# Publication place field and derived country- and geoinformation
source("publication_place.R")
```

# Publication places

### 2022-09-19 inst/examples/publisher.Rmd
Slight changes to scripts for bookdown compatibility

---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: md_document
---

### Publishers

>>>>

---
title: "Publisher preprocessing summary"
author: "Helsinki Computational History Group (COMHIS)"
date: "`r Sys.Date()`"
output: md_document
---

```{r source-publisher, include=FALSE, eval=knit_bookdown}
# publisher field
source("publisher.R")
```

# Publishers

### 2022-09-19 inst/examples/subject_geography.Rmd
Slight changes to scripts for bookdown compatibility

### Subject geographical places

@@

```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

>>>>

```{r source-subject-geography, include=FALSE, eval=knit_bookdown}
# note_subject_topic field
source("subject_geography.R")
```

# Subject geographical places

@@

```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10, eval=FALSE}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

### 2022-09-19 inst/examples/subject_topic.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "subject_topic", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$subject_topic)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-subject-topic, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-subject-topic, include=FALSE, eval=knit_bookdown}
# note_subject_topic field
source("subject_topic.R")
```

# Subject topic

@@

```{r summarytitle-subject-topic, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "subject_topic", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-subject-topic, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$subject_topic)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/successor.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, field, ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df[[field]])
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-successor, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-successor, include=FALSE, eval=knit_bookdown}
# successor field
source("successor.R")
```

# Successor

@@

```{r summarytitle-successor, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, field, ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-successor, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df[[field]])
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/title.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$title)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-title, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-title, include=FALSE, eval=knit_bookdown}
# Title fields
source("title.R")
```

# Title

@@

```{r summarytitle-title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$title)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/title_uniform.Rmd
Slight changes to scripts for bookdown compatibility

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title_uniform", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$title)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-title-uniform, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-title-uniform, include=FALSE, eval=knit_bookdown}
# Title fields
source("title_uniform.R")
```

# Title uniform

@@

```{r summarytitle-title-uniform, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title_uniform", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-title-uniform, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$title)
d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-09-19 inst/examples/uncontrolled.Rmd
Slight changes to scripts for bookdown compatibility

---
title: "uncontrolled"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

@@

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "uncontrolled", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$uncontrolled)
d <- data.frame(title = names(tab), n = as.numeric(tab))

>>>>

```{r setup-uncontrolled, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

```{r source-uncontrolled, include=FALSE, eval=knit_bookdown}
# uncontrolled field
source("uncontrolled.R")
```

# Uncontrolled

@@

```{r summarytitle-uncontrolled, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "uncontrolled", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

@@

```{r uniquetitles-uncontrolled, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$uncontrolled)
d <- data.frame(title = names(tab), n = as.numeric(tab))
